Different forms of uncertainty differently affect the evolution of social learning

### 2022-08-29 ms.tex
Updates from Overleaf

        $\meanG$ & Mean number of generations to convergence & 100k / 8 max. \\
        \bottomrule
    \end{tabular}
\end{table}

@@

We performed sensitivity analyses to ensure that our main analysis is reasonably
robust to a range of auxiliary parameters. \ps{Say these are presented in the supplementary material?} First, we varied the population size, $N$, to explore whether smaller $N$ would show more drift due to finite population size effects. %, but  still generally support our main conclusions. 
Next, we varied the number of prospective teachers, $N_T \in \{2, 10, 20\}$, to supplement the main results that used $N_T = 5$. The number of prospective
teachers should not change whether social learning is optimal, but it may induce more drift since the benefit of social learning may
be more difficult to detect with fewer prosopective teachers. Finally, we varied the
softmax greediness parameter $\beta \in \{1, 100\}$ to supplement the main results
that used $\beta = 10$. We do not
expect agents with different $\beta$ to perform equally well 
individually, so certain $\beta$ values may themselves suppress social learning
by undermining individual learning. Nonetheless, our results
should be valid over some range of $\beta$.

>>>>

        $\meanG$ & Mean number of generations to convergence & max 100k / 8 \\
        \bottomrule
    \end{tabular}
\end{table}

@@

We performed sensitivity analyses to ensure that our main analysis is reasonably
robust to a range of auxiliary parameters. \ps{Say these are presented in the supplementary material?} First, we varied the population size, $N$, to explore whether smaller $N$ would show more drift due to finite population size effects. %, but  still generally support our main conclusions. 
Next, we varied the number of prospective teachers, $N_T \in \{2, 10, 20\}$, to supplement the main results that used $N_T = 5$. The number of prospective
teachers should not change whether social learning is optimal, but it may induce more drift since the benefit of social learning may
be more difficult to detect with fewer prospective teachers. Finally, we varied the
softmax greediness parameter $\beta \in \{1, 100\}$ to supplement the main results
that used $\beta = 10$. We do not
expect agents with different $\beta$ to perform equally well 
individually, so certain $\beta$ values may themselves suppress social learning
by undermining individual learning. Nonetheless, our results
should be valid over some range of $\beta$.
